---
output: github_document
---
<!-- setup-project.md is generated from setup-project.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

I recommend as the first step, opening RStudio: File > New Project (and checking "Create a git repository"). You might also be creating a new repository in github: https://github.com/southwick-associates

### Use package renv

This isolates the R version and packages used for this project from your other projects.

```{r}
# install if you don't have this package
renv::init()
```

### Populate with Template Files

Use `workflow::init()` to populate the project with template files

```{r}
install.packages("remotes")
remotes::install_github("southwick-associates/workflow")
workflow::init()
```

### Run scripts

Use `workflow::run()` to source R scripts with log files stored as .md (use `workflow::run_html()` to store as .html)

```{r}
# write some code to an R file
workflow::run("code/1-test.R")
```

